### 2021-11-05 NSF2021/Description/specificaim3.tex
yny

\subsubsection{Dynamics of a single Janus particle in ionic solutions}
In experiments, Janus particles are often immersed in a solution of ions \cite{ChenWhitmer2011_Sci} or surfactants \cite{}.
In electrolytic solutions the interaction between salt and Janus particle gives 
rise to a slip velocity (on the particle surface) that depends on the ion distribution and the zeta potential \cite{BayatiJCP2016} 
(the potential difference between the Janus particle surface and the surrounding conducting fluid).
The short-range interactions between Janus particles depend on the salt concentration:
At very low salt concentrations, Janus particles repel one another electrostatically, whereas at high salt concentration, van der Waals
forces cause Janus particles to aggregate irreversibly \cite{Goodwin2019}. At intermediate concentrations of monovalent salt, Janus particles are found to self assemble in the form of a small number of elemental units of building blocks \cite{Chen2011_Science}. 
%
\begin{wrapfigure}[11]{l}{0.47\textwidth}
\centerline{\includegraphics[width=0.46\textwidth]{Figures/fig2A_Chen2011_Science}}
  \vspace{-5pt}
\caption{\label{fig:helices_of_JPs} \footnotesize Formation of helices of Janus particles as salt concentration increases \cite{Chen2011_Science}.}
\end{wrapfigure}
%
Figure~\ref{fig:helices_of_JPs} shows that Janus particles can self-assemble into a helix at high concentration of monovalent salt (NaCl) when the density of Janus particles is low to moderate. At high density, JPs are found to form wormlike structures

The Stokes equations in~\eqref{eq:stokes} are modified to incorporate the transport of ions as
\begin{equation}
\label{eq:stokes}
\begin{aligned}
  &-\mu \Delta \mathbf{u} + \nabla p = \Delta\psi\cdot\nabla\psi, \quad \mathbf{x} \in \Omega, \qquad
  \nabla \cdot \mathbf{u} = 0,  \quad \mathbf{x} \in \Omega,\\
  &\delta^2\Delta\psi = -\frac{1}{2}\left(n_+-n_-\right),\qquad
  \frac{\partial n_{\pm}}{\partial t} + \nabla\cdot{\bf j}_{\pm} = 0,\\
  &{\bf j}_{\pm} = -\nabla n_{\pm \mp n_{\pm} \nabla\psi + Pe n_{\pm}\mathbf{u}.
\end{aligned}
\end{equation}
The screen length $\rho$ is now a function of the ion concentrations: $\rho = \rho(n_+,n_-)$.

>>>>

\subsubsection{Dynamics of a single Janus particle in ionic solutions}
In experiments, Janus particles are often immersed in a solution of ions \cite{ChenWhitmer2011_Sci} or surfactants \cite{}.
In electrolytic solutions the interaction between salt and Janus particle gives 
rise to a slip velocity (on the particle surface) that depends on the ion distribution and the zeta potential \cite{BayatiJCP2016} 
(the potential difference between the Janus particle surface and the surrounding conducting fluid).
The short-range interactions between Janus particles depend on the salt concentration:
At very low salt concentrations, Janus particles repel one another electrostatically, whereas at high salt concentration, van der Waals
forces cause Janus particles to aggregate irreversibly \cite{Goodwin2019}. At intermediate concentrations of monovalent salt, Janus particles are found to self assemble in the form of a small number of elemental units of building blocks \cite{Chen2011_Science}. 
%
\begin{wrapfigure}[6]{l}{0.47\textwidth}
\centerline{\includegraphics[width=0.46\textwidth]{Figures/fig2A_Chen2011_Science}}
  \vspace{-5pt}
\caption{\label{fig:helices_of_JPs} \footnotesize Formation of helices of Janus particles as salt concentration increases \cite{Chen2011_Science}.}
\end{wrapfigure}
%
Figure~\ref{fig:helices_of_JPs} shows that Janus particles can self-assemble into a helix at high concentration of monovalent salt (NaCl) when the density of Janus particles is low to moderate. At high density, JPs are found to form wormlike structures

The Stokes equations in~\eqref{eq:stokes} are modified to incorporate the transport of ions as
\begin{equation}
\label{eq:stokes}
\begin{aligned}
  &-\Delta \mathbf{u} + \nabla p = \Delta\psi\cdot\nabla\psi, \qquad
  \nabla \cdot \mathbf{u} = 0,  \quad \mathbf{x} \in \Omega,\\
  &\delta^2\Delta\psi = -\frac{1}{2}\left(n_+-n_-\right),\qquad
  \frac{\partial n_{\pm}}{\partial t} + \nabla\cdot{\bf j}_{\pm} = 0,\\
  &{\bf j}_{\pm} = -\nabla n_{\pm} \mp n_{\pm} \nabla\psi + \mbox{Pe} n_{\pm}\mathbf{u},
\end{aligned}
\end{equation}
where $\delta$ is the Debye length, $\mbox{Pe}$ is the Peclet number, a ratio between the convection and  thermal diffusion time scales.
$n_{+}$ ($n_{-}$) is the concentration of cation (anion).
The screen length $\rho$ in the HAP model is now a function of the ion concentrations: $\rho = \rho(n_+,n_-)$.
